---
title: "Manuscript results"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning=F, message=F)
#rm(list = ls())
options(scipen=999)
```

```{r required packages}
require(tidyverse)    # for data manipulation
require(formattable)  # for formatting tables
require(knitr)        # for saving tables
require(scales)       # for ggplot axis labels
library(gridExtra)    # for gridded plots 
require(survival)     # for survival analysis
require(survminer)    # for survival plotting
```

compare survival curves (input and output)

time from 1st progression to model start (diagnosis to 1st prog or 1st prog to 2nd prog)

time to death

survival curves best/2nd best: choose the one that best reflects clinicians input (rather than AIC/BIC), use Exponential (force things to go down quicker, as clinicians don't expect the flattening)

discounting scenarios and 2nd-best distribution


## Data location

```{r}
fileloc <- here::here("04_analysis","output","scenarios","basecase exp lifetime combo")
nn <- 50
```

The files are spread out over 5 folders. 

## Table 2 & Abstract

Coding the following: 

Table 2:Estimates of life-years after diagnosis, QALYs (Discounted) and Costs (Discounted) Estimates reported with 95% Confidence Interval in brackets. All costs are given in Canadian dollars.

Abstract results

```{R}
# model results 
#res_model <- list.files(paste0(fileloc, "/Scenario 1 life-time treatment", "/res_model"),full.names = TRUE)
#res_model <- list.files(paste0(here::here("04_analysis","output"), "/res_model"),full.names = TRUE)[1:5]
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[1:nn]
#res_model <- list.files(paste0(fileloc, "output/rad_after_prog2_lifetime_discount20", "/res_model"),full.names = TRUE)
#res_model <- list.files(paste0(fileloc, "output/rad_after_prog2_lifetime_discount30", "/res_model"),full.names = TRUE)

#res_model <- list.files(paste0(fileloc, "output/rad_after_prog2_2yrs", "/res_model"),full.names = TRUE)
#res_model <- list.files(paste0(fileloc, "output/rad_after_prog2_2yrs_discount20", "/res_model"),full.names = TRUE)
#res_model <- list.files(paste0(fileloc, "output/rad_after_prog2_2yrs_discount30", "/res_model"),full.names = TRUE)

# turning into dataframe
df_model  <- map_df(res_model, readRDS) 
df_model <- df_model %>% filter(subset == "all")
# creating a key in the same format as the one in correct_surv
df_model <- df_model %>% 
  mutate(key = paste0(sim,"_",rr))

# fixing survival for everyone who doesn't have a correct survival time
df_model <- df_model %>% 
    mutate( Value = ifelse(Variable == "LY", 80-Value, Value))

# no longer need key 
df_model <- df_model %>%
  select(-key)
```

```{r}
df_output <- df_model %>% filter(discount == 1) %>% select(-rr)
# df_output$intervention[df_output$intervention == "SoC"] <- "Targeted"
df_output1 <- df_output %>% group_by(Variable, Type) %>% summarise(Mean = mean(Value))
write.csv(df_output1, "output.csv", row.names = F)
```

```{r}
df_delta <- df_model %>% 
  spread(intervention, Value) %>%   
  mutate(Delta = Targeted-SoC) %>% 
  select(-Targeted,-SoC)

df_model <- df_model %>% 
  group_by(Variable, Type, subset, intervention, discount, rr) %>% 
  summarise( mean = mean(Value),
             q025 = quantile(Value, 0.025),
             q975 = quantile(Value, 0.975)) %>% ungroup()
df_model <-df_model %>% 
  mutate(mean = case_when(Variable == "Cost"~ paste0(currency(mean,
                                                              symbol = "\\$" ,digits = 0)),
                          Variable != "Cost"~ paste0(round(mean, 2))),
         q025 = case_when(Variable == "Cost"~ paste0(currency(q025, symbol = "\\$" ,digits = 0)),
                          Variable != "Cost"~ paste0(round(q025, 2))),
        q975 = case_when(Variable == "Cost"~ paste0(currency(q975, symbol = "\\$" ,digits = 0)),
                          Variable != "Cost"~ paste0(round(q975, 2))                  
                          )
         ) %>% 
  mutate( stat = paste0(mean, " (", q025, ";",q975,")"))

df_model1 <- df_model %>% 
  select(-mean, - q025, -q975)


df_delta1 <- df_delta %>% rename(Value = Delta) %>% 
  group_by(Variable, Type, subset, discount, rr) %>% 
  summarise( mean = mean(Value),
             q025 = quantile(Value, 0.025),
             q975 = quantile(Value, 0.975)) %>% ungroup() %>% 
  mutate(mean = case_when(Variable == "Cost"~ paste0(currency(mean, symbol = "\\$" ,digits = 0)),
                          Variable != "Cost"~ paste0(round(mean, 2))),
         q025 = case_when(Variable == "Cost"~ paste0(currency(q025, symbol = "\\$" ,digits = 0)),
                          Variable != "Cost"~ paste0(round(q025, 2))),
        q975 = case_when(Variable == "Cost"~ paste0(currency(q975, symbol = "\\$" ,digits = 0)),
                          Variable != "Cost"~ paste0(round(q975, 2))               
                         
                          )
         ) %>% 
  mutate( stat = paste0(mean, " (", q025, ";",q975,")")) %>% 
    select(-mean, - q025, -q975)

df_deltacea <- df_delta %>% 
    filter(Type == "Total" | Type == "QALY", subset == "all", discount == 1 ) %>% select(-Type)  %>% spread(Variable, Delta)

df_model2 <- df_model1 %>% 
  bind_rows(mutate( df_delta1, intervention = "delta")) %>% 
    mutate(Variable = factor(Variable, levels = c("LY","QALY","Cost")),
         Type = factor(Type, levels = c("LY","QALY","Total","PLGG","AE","Treatment","Radiation"))
         ) %>% 
  arrange(Variable, Type, discount, rr) %>% 
  spread(intervention, stat)

df_model3 <- df_model2 %>% 
  arrange(subset, rr, Variable, Type, discount )



tb2 <-df_model3  %>%
  filter(subset == "all") %>% 
  filter( !(Variable == "Cost" & discount == 0),
          !(Variable == "QALY" & discount == 0) ) %>%
  select(-Variable, - subset,-discount  ) %>% 
  rename(Variable = Type,
         Delta = delta,
         intervention = Targeted,
         control = SoC) 
```

**Table 2**: 

```{r}
library(pander)
library(forcats)

# kable(tb2)
tb2a <- tb2 %>% 
  mutate(Variable = fct_recode(Variable, `Life-years` = "LY", 
                               QALY = "QALY",
                               `Total Cost` = "Total")) %>%
  #select(Variable, intervention, control, Delta , rr)
  select(Variable, intervention, control, Delta )
tb2a$Variable <- as.character(tb2a$Variable)
tb2a$Variable[tb2a$Variable=="Treatment"] <- "Targeted costs"
tb2a$Variable[tb2a$Variable=="PLGG"] <- "Non-Targeted PLGG related costs"
tb2a$Variable[tb2a$Variable=="AE"] <- "AE related costs"
tb2a$Variable[tb2a$Variable=="Radiation"] <- "Radiation costs"
tb2a$Variable <- factor(tb2a$Variable, levels = c("Life-years","QALY","Total Cost","Non-Targeted PLGG related costs",
                                                  "AE related costs","Targeted costs","Radiation costs"))
pander(tb2a)
``` 

```{r}
# Averaging cohort traces across simulation run
l_prop_df <- list.files(paste0(fileloc, "/trace"),full.names = TRUE)[1:nn]
prop_df  <- map_df(l_prop_df[1], readRDS) 
prop_df$cycle <- as.numeric(prop_df$cycle)
prop_df$intervention <- ifelse(prop_df$intervention == "Targeted", 1, 0)
prop_df <- apply(prop_df,2,as.numeric)
prop_df <- as.data.frame(prop_df)
prop_df <- prop_df %>% dplyr::select("cycle", "pre_prog", "auditory", "cardiovascular", "death_outside", 
                                             "death_plgg", "neurologic", "prog1", "SN", "stroke", "visual", "death_cardio",
                                             "prog2", "SN_gen", "death_SN", "death_stroke", "cardiovascular_gen",
                                             "stroke_gen", "intervention")
if (nn > 1) {
  for (i in 2:nn) {
    prop_df_i  <- map_df(l_prop_df[i], readRDS) 
    prop_df_i$cycle <- as.numeric(prop_df_i$cycle)
    prop_df_i$intervention <- ifelse(prop_df_i$intervention == "Targeted", 1, 0)
    prop_df_i <- prop_df_i %>% dplyr::select("cycle", "pre_prog", "auditory", "cardiovascular", "death_outside", 
                                             "death_plgg", "neurologic", "prog1", "SN", "stroke", "visual", "death_cardio",
                                             "prog2", "SN_gen", "death_SN", "death_stroke", "cardiovascular_gen",
                                             "stroke_gen", "intervention")
    prop_df_i <- apply(prop_df_i,2,as.numeric)
    prop_df_i <- as.data.frame(prop_df_i)
    prop_df <- prop_df + prop_df_i
  }
  prop_df <- prop_df/nn
}
prop_df$intervention <- ifelse(prop_df$intervention == 1, "Targeted", "SoC")

prop_long <- prop_df %>% select(cycle, pre_prog, prog1, prog2, death_plgg, intervention) %>%
  tidyr::pivot_longer(-c(cycle,intervention), names_to = "state", values_to = "proportion") %>%
  mutate(state=case_when(state=="pre_prog"~"Pre-progression",
                         state=="prog1" ~ "1st progression",
                         state=="prog2" ~ "2nd+ progression",
                         state=="death_plgg" ~ "PLGG-related death"),
         state=factor(state, levels=c("Pre-progression", "1st progression", "2nd+ progression", "PLGG-related death")),
         cycle=cycle/12)
ggplot(data = prop_long, aes(x = cycle, y = proportion, color = state, group = state)) +
  geom_line() +
  labs(title = "Trace Plot of PLGG States Across Cycles",
       x = "Year",
       y = "Proportion",
       color = "PLGG state") +
  scale_color_manual(values = c("green","orange","red","navy")) + 
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, by = 0.1)) +
  scale_x_continuous(limits = c(0, 80), breaks = seq(0, 80, by = 10)) +
  #geom_hline(yintercept=0.4, linetype="dashed", color = "purple") +
  #geom_vline(xintercept=25, linetype="dashed", color = "purple") +
  theme_bw() +
  theme(legend.position = "right") + 
  facet_wrap(~intervention)
```

```{r}
# AEs
l_AE_df <- list.files(paste0(fileloc, "/AE_track"),
                      full.names = TRUE)[1:nn]
AE_df <- map_df(l_AE_df[1], readRDS) 
## Targeted
AE_df_Targeted <- AE_df %>% filter(intervention == "Targeted")
AE_prop_Targeted <-apply(AE_df_Targeted %>% dplyr::select(-intervention), 2, function(x){prop.table(table(x))})
df_AE_Targeted <- data.frame(cycle=0:960)
df_AE_Targeted$cycle <- as.factor(df_AE_Targeted$cycle)
for (i in 1:length(AE_prop_Targeted)){
  df_AE_prop <- as.data.frame(AE_prop_Targeted[[i]])
  colnames(df_AE_prop) <- c("cycle",names(AE_prop_Targeted)[i])
  df_AE_Targeted <- df_AE_Targeted %>% left_join(df_AE_prop, by = c("cycle"))
}
df_AE_Targeted[1,-1] <- 0
df_AE_Targeted$cycle <- as.numeric(df_AE_Targeted$cycle)
df_AE_Targeted[is.na(df_AE_Targeted)] <- 0
if (nn == 1) {
  df_AE_Targeted$intervention <- "Targeted"
}

if (nn > 1) {
  for (i in 2:nn) {
    AE_df <- map_df(l_AE_df[i], readRDS) 
    AE_df_Targeted_i <- AE_df %>% filter(intervention == "Targeted")
    AE_prop_Targeted_i <-apply(AE_df_Targeted_i %>% dplyr::select(-intervention), 2, function(x){prop.table(table(x))})
    df_AE_Targeted_i <- data.frame(cycle=0:960)
    df_AE_Targeted_i$cycle <- as.factor(df_AE_Targeted_i$cycle)
    for (j in 1:length(AE_prop_Targeted_i)){
      df_AE_prop <- as.data.frame(AE_prop_Targeted_i[[j]])
      colnames(df_AE_prop) <- c("cycle",names(AE_prop_Targeted_i)[j])
      df_AE_Targeted_i <- df_AE_Targeted_i %>% left_join(df_AE_prop, by = c("cycle"))
    }
    df_AE_Targeted_i[1,-1] <- 0
    df_AE_Targeted_i$cycle <- as.numeric(df_AE_Targeted_i$cycle)
    df_AE_Targeted_i[is.na(df_AE_Targeted_i)] <- 0
    df_AE_Targeted <- df_AE_Targeted + df_AE_Targeted_i
  }
  df_AE_Targeted <- df_AE_Targeted/nn
  df_AE_Targeted$intervention <- "Targeted"
}
## SoC
AE_df_SoC <- AE_df %>% filter(intervention == "SoC")
AE_prop_SoC <-apply(AE_df_SoC %>% dplyr::select(-intervention), 2, function(x){prop.table(table(x))})
df_AE_SoC <- data.frame(cycle=0:960)
df_AE_SoC$cycle <- as.factor(df_AE_SoC$cycle)
for (i in 1:length(AE_prop_SoC)){
  df_AE_prop <- as.data.frame(AE_prop_SoC[[i]])
  colnames(df_AE_prop) <- c("cycle",names(AE_prop_SoC)[i])
  df_AE_SoC <- df_AE_SoC %>% left_join(df_AE_prop, by = c("cycle"))
}
df_AE_SoC[1,-1] <- 0
df_AE_SoC$cycle <- as.numeric(df_AE_SoC$cycle)
df_AE_SoC[is.na(df_AE_SoC)] <- 0
if (nn == 1) {
  df_AE_SoC$intervention <- "SoC"
}

if (nn > 1) {
  for (i in 2:nn) {
    AE_df <- map_df(l_AE_df[i], readRDS) 
    AE_df_SoC_i <- AE_df %>% filter(intervention == "SoC")
    AE_prop_SoC_i <-apply(AE_df_SoC_i %>% dplyr::select(-intervention), 2, function(x){prop.table(table(x))})
    df_AE_SoC_i <- data.frame(cycle=0:960)
    df_AE_SoC_i$cycle <- as.factor(df_AE_SoC_i$cycle)
    for (j in 1:length(AE_prop_SoC_i)){
      df_AE_prop <- as.data.frame(AE_prop_SoC_i[[j]])
      colnames(df_AE_prop) <- c("cycle",names(AE_prop_SoC_i)[j])
      df_AE_SoC_i <- df_AE_SoC_i %>% left_join(df_AE_prop, by = c("cycle"))
    }
    df_AE_SoC_i[1,-1] <- 0
    df_AE_SoC_i$cycle <- as.numeric(df_AE_SoC_i$cycle)
    df_AE_SoC_i[is.na(df_AE_SoC_i)] <- 0
    df_AE_SoC <- df_AE_SoC + df_AE_SoC_i
  }
  df_AE_SoC <- df_AE_SoC/nn
  df_AE_SoC$intervention <- "SoC"
}

df_AE <- rbind(df_AE_Targeted, df_AE_SoC)

prop_long <- df_AE %>% select(cycle,auditory,cardiovascular,neurologic,SN,stroke,visual,intervention) %>%
  tidyr::pivot_longer(-c(cycle,intervention), names_to = "state", values_to = "proportion") %>%
  mutate(cycle=cycle/12)
ggplot(data = prop_long, aes(x = cycle, y = proportion, color = state, group = state)) +
  geom_line() +
  labs(title = "Trace Plot of PLGG-related AE States Across Cycles",
       x = "Year",
       y = "Proportion",
       color = "PLGG-related AE states") +
  theme_bw() +
  theme(legend.position = "right") +
  facet_wrap(~intervention) -> a

prop_long <- df_AE %>% select(cycle,SN_gen,cardiovascular_gen,death_outside,death_SN,stroke_gen,death_cardio,death_stroke, 
                                intervention) %>%
  tidyr::pivot_longer(-c(cycle,intervention), names_to = "state", values_to = "proportion") %>%
  mutate(cycle=cycle/12)
ggplot(data = prop_long, aes(x = cycle, y = proportion, color = state, group = state)) +
  geom_line() +
  labs(title = "Trace Plot of Other AE States Across Cycles",
       x = "Year",
       y = "Proportion",
       color = "Other AE states") +
  theme_bw() +
  theme(legend.position = "right") +
  facet_wrap(~intervention) -> b
grid.arrange(a,b, nrow=2, ncol=1)
```

```{r}

```

## Supplementary Table 1 

Supplementary Table 1: Estimates of life-years after diagnosis, QALYs (Discounted) and Costs (Discounted), for fused patients, and fused patients who progressed.

<!-- ```{r} -->

<!-- sm_tb1 <-df_model3  %>% -->
<!--   filter(subset == "fused") %>%  -->
<!--   filter( !(Variable == "Cost" & discount == 0), -->
<!--           !(Variable == "QALY" & discount == 0) ) %>% -->
<!--   select(-Variable,-discount  ) %>%  -->
<!--   rename(Variable = Type, -->
<!--          Delta = delta, -->
<!--          intervention = Targeted, -->
<!--          control = SoC)  -->

<!-- sm_tb1 <- sm_tb1 %>% rename(Control = control, -->
<!--                             Experimental = intervention, -->
<!--                             `Difference (Experimental - Control)` = Delta) -->
<!-- sm_tb1$Variable <- as.character(sm_tb1$Variable) -->
<!-- sm_tb1$Variable[3:7] <- c("Total costs", "Non-targeted therapy PLGG costs", "AE costs", -->
<!--                           "Treatment costs", "Radiation costs") -->

<!-- sm_tb1 %>% select(-subset, -rr) %>% select(Variable, Experimental, Control, `Difference (Experimental - Control)`) %>% -->
<!--   kable() -->
<!-- ``` -->

```{r}

```

<!-- ## Figure 4 Cost-effectiveness plane -->

<!-- Figure 4: Cost-effectiveness plane indicating the incremental cost and incremental effectiveness estimates related to molecular testing for each probabilistic simulation assuming both a no-radiation (n = 1,000) and radiation benefit (n = 1,000) -->

<!-- ```{r} -->
<!-- df_deltacea <- df_delta %>%  -->
<!--     filter(Type == "Total" | Type == "QALY", subset == "fused", discount == 1 ) %>% select(-Type)  %>% spread(Variable, Delta) -->


<!-- df_deltacea1 <- df_deltacea %>%  -->
<!--   mutate(rr =factor(rr, levels = c(0,1), labels = c("No radiation benefit","Radiation benefit")), -->
<!--          type = "all") -->
<!-- df_means <- df_deltacea %>%  -->
<!--   group_by(rr) %>%  -->
<!--   summarise(Cost = mean(Cost), -->
<!--             QALY = mean(QALY)) %>%  -->
<!--   mutate(type = "Mean Values") %>%  -->
<!--   mutate(rr1 = factor(rr, levels = c(0,1), labels = c("No radiation benefit","Radiation benefit") )) -->
<!-- toplot_plane <-df_deltacea1 %>%  -->
<!--   ggplot() +  -->
<!--   geom_point(aes(x = QALY, y = Cost), alpha = 0.75 , size = 0.6) +  -->
<!--   # geom_point(aes(x = QALY, y = Cost), color = "black", data = df_means,shape = 2,show.legend = TRUE, size = 3) +  -->
<!--   geom_hline(yintercept = 0) +  -->
<!--   geom_vline(xintercept = 0) +  -->
<!--   theme_bw() +  -->
<!--   theme(legend.title = element_blank()) + -->
<!--   ylab("Discounted Total Costs") +   -->
<!--   xlab("Discounted QALYs") +  -->
<!--   labs(color = "", shape = "Mean") + -->
<!--   scale_y_continuous(labels = dollar_format(prefix="$")) + -->
<!--   facet_wrap(~ rr) +  -->
<!--   theme( panel.grid.major = element_blank(), -->
<!-- panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) -->


<!-- toplot_plane -->

<!-- ``` -->

<!-- # Figure 2  -->

<!-- Figure 2: Median cumulative incidence of all-cause mortality for all patients assuming n o radiation benefit or with radiation benefit. -->

<!-- ```{r} -->
<!-- res_os <- list.files(paste0(fileloc, "/res_OS"),full.names = TRUE) -->
<!-- df_OS <- map_df(res_os, readRDS) -->

<!-- df_med <- df_OS %>% -->
<!--   group_by(cycle, type, intervention, rr) %>% -->
<!--   summarise(median = median(OS)) %>% ungroup() %>% -->
<!--    mutate(rr = ifelse(rr == 0, "No radiation benefit", "Radiation benefit")) %>% -->
<!--     mutate(intervention  = ifelse(intervention == "Norad_Fused", "Intervention","Control")) -->



<!-- df_delta <- df_OS %>% -->
<!--   spread(intervention, OS) %>% -->
<!--   mutate(delta = (1-Targeted) - (1-SoC)) %>% -->
<!--   select(-Targeted, - SoC) %>% -->
<!--   group_by(cycle, type, rr) %>% -->
<!--   summarise(median = median(delta), -->
<!--             q025 = quantile(delta, 0.025), -->
<!--             q975 = quantile(delta, 0.975)) %>% ungroup() %>%  -->
<!--   mutate(rr = ifelse(rr == 0, "No radiation benefit", "Radiation benefit")) -->


<!-- rm(df_OS) -->


<!-- plot1 <- filter(df_med,type == "OS") %>% -->
<!--   ggplot() +  -->
<!--   geom_line(aes(x = cycle, y = 1-median, linetype = intervention)) + -->
<!--   facet_wrap(~rr) + -->
<!--   theme_bw() +  -->
<!--   ylab("\n Cumulative Incidence, all-cause mortality") +  -->
<!--   xlab("Time from diagnosis, Years")  +  -->
<!--     theme(legend.title =element_blank(),legend.position="top") + -->
<!--   theme( panel.grid.major = element_blank(), -->
<!-- panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) -->

<!-- plot2_delta <- filter(df_delta,type == "OS" ) %>% -->
<!--   mutate(t1 = "Median (95% CI)") %>%  -->
<!--   ggplot() +  -->
<!--   geom_line(aes(x = cycle, y = median, color = t1)) +  -->
<!--   geom_ribbon(aes(x = cycle, ymin = q025, ymax = q975, fill = t1), alpha = 0.3,show.legend = T) + -->
<!--   facet_wrap(~rr) + theme_bw() + -->
<!--   ylab("Delta (Intervention - Control) \n Cumulative Incidence, all-cause mortality") +  -->
<!--     xlab("Time from diagnosis, Years") +  -->
<!--   theme(legend.title =element_blank(),legend.position="top")  + -->
<!--   scale_color_manual(values = "black") + -->
<!--   scale_fill_manual( values = "black") + -->
<!--   theme( panel.grid.major = element_blank(), -->
<!-- panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) -->



<!-- fig2 <-grid.arrange(plot1, plot2_delta) -->

<!-- fig2 -->
<!-- ``` -->

<!-- In text results -->

<!-- ```{r} -->
<!-- df_med %>%  -->
<!--   filter(cycle == 20) %>% mutate(median = median*100) %>%  -->
<!--   spread(intervention, median) %>%  -->
<!--   arrange(rr, type) %>% filter(type == "OS" | type == "Fused") %>%   -->
<!--   kable(digits = 1 )  -->
<!-- ``` -->

<!-- # Supp Fig 1 -->

<!-- Supplementary Figure 1: Cumulative incidence of all-cause mortality for all fused patients, and for fused patients who progressed -->

<!-- ```{r} -->
<!-- plot2SM <-filter(df_delta,type != "OS" ) %>% -->
<!--   mutate(type = factor(type, levels = c("Fused","FusedProg"), -->
<!--                        labels = c("Fused patients", "Fused patients that progressed"))) %>%  -->
<!--  mutate(t1 = "Median (95% CI)") %>%  -->
<!--   ggplot() +  -->
<!--   geom_line(aes(x = cycle, y = median, color = t1)) +  -->
<!--   geom_ribbon(aes(x = cycle, ymin = q025, ymax = q975, fill = t1), alpha = 0.3,show.legend = T) + -->
<!--   facet_wrap(~rr + type,) + theme_bw() + -->
<!--   ylab("Delta (Intervention - Control) \n Cumulative Incidence, all-cause mortality") +  -->
<!--     xlab("Time from diagnosis, Years") +  -->
<!--   theme(legend.title =element_blank(),legend.position="top")  + -->
<!--   scale_color_manual(values = "black") + -->
<!--   scale_fill_manual( values = "black")  + -->
<!--   theme( panel.grid.major = element_blank(), -->
<!-- panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) -->

<!-- plot2SM -->

<!-- rm(fig2) -->
<!-- ``` -->

<!-- ## Figure 3  -->

<!-- Create figure 3  -->

<!-- First accounting for mortality  -->

<!-- ```{r eval=T, message=FALSE, warning=FALSE, include=FALSE} -->
<!-- res_CI <- list.files(paste0(fileloc, "/res_CI"),full.names = TRUE) -->
<!-- res_OS <- list.files(paste0(fileloc, "/res_OS"),full.names = TRUE) -->

<!-- res_CI_s <- list.files(paste0(fileloc, "/res_CI"),full.names = FALSE) -->
<!-- res_OS_s <- list.files(paste0(fileloc, "/res_OS"),full.names = FALSE) -->

<!-- res_OS <- res_OS[order(res_OS_s)] -->
<!-- res_CI <- res_CI[order(res_CI_s)] -->


<!-- res_short <- list.files(paste0(fileloc, "/res_CI"),full.names = F) -->
<!-- res_short <- res_short[order(res_OS_s)] -->
<!-- v_n <-c( "neurologic", "auditory", "visual", "stroke", "cardiovascular", "SN") -->

<!-- ## first read in first thing  -->

<!-- for( i in seq_along(res_short)){ -->
<!--   if(i %% 10 == 0){message(i/length(res_short))} -->
<!-- tempCI <- readRDS(res_CI[i]) -->
<!-- tempOS <- readRDS(res_OS[i]) %>% rename(time = cycle) %>% filter(type == "OS") -->
<!-- tempOS <-tempOS %>% group_by(type, sim , intervention, rr) %>%  -->
<!--   mutate(OS_t1 = lag(OS, 1,1)) %>%  -->
<!--   select(-type) -->


<!-- tempCI <- tempCI %>%  -->
<!--   left_join(tempOS, by = c("time", "sim", "intervention", "rr")) -->

<!-- calcCI <- tempCI %>%  -->
<!--   filter(state %in% v_n) %>% -->
<!--     mutate(ci = (ceiling(ci*100000)*ceiling(OS*100000))/100000) %>%  -->
<!--     mutate(ci = ceiling(ci*100000), -->
<!--            OS = ceiling(OS*100000), -->
<!--            OS_t1= ceiling(OS_t1*100000)/100000) %>% -->
<!--   group_by(state, intervention, rr ) %>% -->
<!--   mutate(ci = c(0,diff(ci,1))) %>%  -->
<!--   mutate(mcf =  ci/OS, -->
<!--          CI = mcf*OS_t1 -->
<!--          ) %>%  -->
<!--   mutate(cumCI = cumsum(CI))  %>% -->
<!--   select(state, intervention ,rr, time,cumCI, sim ) %>% ungroup() -->

<!-- for(state1 in v_n){ -->
<!--   dir.create(path = here::here("05_report","1newCIcalc",state1),recursive = T) -->

<!--      filter(calcCI, state == state1) %>% -->
<!--       saveRDS(file = here::here("05_report","1newCIcalc",state1,"/",paste0(state1,i,"BIG.RDS"))) -->


<!-- } -->

<!-- } -->


<!-- ``` -->

<!-- ```{r} -->
<!-- store_toplot <- vector(mode = "list", length = length(v_n)) -->


<!-- for(j in seq_along(v_n)){ -->
<!--   message(j) -->

<!--   list_files_instate <- list.files(here::here("05_report","1newCIcalc",v_n[j]),full.names = TRUE) -->

<!-- big1   <- map_df(list_files_instate, readRDS) -->

<!-- store_toplot[[j]] <- big1 %>%  -->
<!--   group_by(intervention, state,rr) %>% -->
<!--   group_by(intervention, state,rr) %>% -->
<!--   mutate(cumCI = ifelse(is.nan(cumCI) , NA, cumCI  )) %>% -->
<!--   fill(cumCI,.direction = "down") %>% -->
<!--   group_by(intervention, state, rr,  time  ) %>% -->
<!-- summarise(median = median(cumCI), -->
<!--           q025 = quantile(cumCI, 0.025), -->
<!--           q975 = quantile(cumCI, 0.975)) %>% ungroup() -->

<!-- } -->

<!-- unlink(here::here("05_report","1newCIcalc"),recursive = T) -->

<!-- ``` -->

<!-- ```{r} -->

<!-- toplotCI <- do.call(rbind,store_toplot) -->

<!-- plotCI <- toplotCI %>% ungroup() %>% -->
<!--     mutate(intervention  = ifelse(intervention == "Norad_Fused", "Intervention","Control")) %>%  -->
<!--     mutate(rr= ifelse(rr == 1, "Cherlow, et al.","No radiation benefit")) %>% -->
<!--   ggplot() +  -->
<!--   geom_line(aes(x = time, y = median, color = intervention)) +   geom_ribbon(aes(x = time, ymin = q025, ymax = q975 , fill = intervention), alpha = 0.3,show.legend = T) + -->
<!--  facet_grid(rows =  vars(state) , cols =  vars(rr) ) + -->
<!-- theme_bw() + -->
<!--   ylab("Cumulative incidence, Treatment related AE") +  -->
<!--     xlab("Time from diagnosis, Years") +  -->
<!--   theme( panel.grid.major = element_blank(), -->
<!-- panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) -->

<!-- plotCI -->
<!-- ``` -->

<!-- ```{r} -->

<!-- dir.create(here::here("05_report","tempfold1")) -->
<!-- res_CI <- list.files(paste0(fileloc, "/res_CI"),full.names = TRUE) -->
<!-- res_OS <- list.files(paste0(fileloc, "/res_OS"),full.names = TRUE) -->

<!-- res_CI_s <- list.files(paste0(fileloc, "/res_CI"),full.names = FALSE) -->
<!-- res_OS_s <- list.files(paste0(fileloc, "/res_OS"),full.names = FALSE) -->

<!-- res_OS <- res_OS[order(res_OS_s)] -->
<!-- res_CI <- res_CI[order(res_CI_s)] -->


<!-- res_short <- list.files(paste0(fileloc, "/res_CI"),full.names = F) -->
<!-- res_short <- res_short[order(res_OS_s)]  -->

<!-- list1 <- c("stroke_gen","cardiovascular_gen","SN_gen") -->
<!-- list2 <- c("stroke","cardiovascular","SN") -->
<!-- v_n <- c(list1,list2) -->

<!-- ## first read in first thing  -->

<!-- for( i in 1:length(res_short)){ -->
<!--   if(i %% 10 == 0){message(i/length(res_short))}  -->
<!--   tempCI <- readRDS(res_CI[i])  -->
<!--   tempOS <- readRDS(res_OS[i]) %>%  -->
<!--     rename(time = cycle) %>% filter(type == "OS") -->

<!--   tempOS <-tempOS %>% group_by(type, sim , intervention, rr) %>% -->
<!--   mutate(OS_t1 = lag(OS, 1,1)) %>% -->
<!--   select(-type) -->


<!-- tempCI <- tempCI %>% -->
<!--   left_join(tempOS, by = c("time", "sim", "intervention", "rr")) -->

<!-- ## Have TempCI joined with tempOS -->
<!-- ## issue is that i calcualted CI = cumsum(mean(incidence*OS)) ##  mean(abs(mDur1[,ci_states[j]] - time_v[t1]) < tol)/per_alive[t1] ## cumsum(k1) ## Reversing that -->

<!-- calCI <-tempCI %>% -->
<!--   filter(state %in% v_n) %>% -->
<!--   group_by(state, sim, intervention ,rr, type) %>%arrange(time) %>% -->
<!--   mutate(i = c(0, diff(ci)), -->
<!--          i = (i*100000)*OS, -->
<!--          ) %>% ungroup() %>% -->
<!--   mutate(state = case_when( -->
<!-- state == list1[1] |state ==  list2[1] ~ list2[1], state == list1[2] |state ==  list2[2] ~ list2[2], state == list1[3] |state ==  list2[3] ~ list2[3] -->
<!-- )) %>%  -->
<!--    group_by(state, sim, intervention ,rr, type, time) %>% -->
<!--   mutate( i = sum(i)) %>%  ungroup() %>%  -->
<!--    group_by(state, sim, intervention ,rr, type) %>% -->
<!--    mutate(mcf =  i /(OS*100000), -->
<!--          CI = mcf*OS_t1 -->
<!--          )  %>%  -->
<!--     mutate(cumCI = cumsum(CI))  %>% -->
<!--   select(state, intervention ,rr, time,cumCI, sim, type )  -->

<!-- # trying to fix that cumulative incidence doesnt take into account mortality  -->


<!--       saveRDS(file = here::here("05_report","tempfold1",paste0(i,"BIG.RDS")),object = calCI)  -->
<!--       }  -->
<!-- ``` -->

<!-- ```{r} -->

<!-- file1 <- list.files(here::here("05_report","tempfold1"),full.names = T) -->

<!-- bigdf<-map_df(file1, readRDS) -->

<!-- bigdf %>% arrange(desc(cumCI)) -->

<!-- bigdf %>%  -->
<!--    mutate(rr = ifelse(rr == 0, "No radiation benefit", "Radiation benefit")) %>% -->
<!--     mutate(intervention  = ifelse(intervention == "Targeted", "Intervention","Control")) %>% -->
<!--   group_by(state, intervention, rr, time,type) %>%  -->
<!--   summarise(mean = mean(cumCI), -->
<!--             q025 = quantile(cumCI,0.025), -->
<!--             q975 = quantile(cumCI,0.975)) %>%  -->

<!--   ggplot() + -->
<!--   facet_wrap(~state+ rr) + geom_line(aes(x = time, y= mean, color = intervention)) + -->
<!--   geom_ribbon(aes(x = time, ymin = q025, ymax = q975, fill = intervention), alpha = 0.1)+ -->
<!--   theme_bw() -->

<!-- unlink(here::here("05_report","tempfold1"),recursive = T) -->

<!-- ``` -->


<!-- ```{r} -->
<!-- icd_10_death <- c("O95", "O96", "O97", "R96", "R97", "R98", "R99") -->
<!-- Df_full$icd_death <- rep(0, nrow(Df_full)) -->
<!-- for (i in 1:nrow(Df_full)) { -->
<!--   if (substr(Df_full$DIAG_CODE_1[i], 1, 3) %in% icd_10_death |  -->
<!--       substr(Df_full$DIAG_CODE_2[i], 1, 3) %in% icd_10_death | -->
<!--       substr(Df_full$DIAG_CODE_3[i], 1, 3) %in% icd_10_death | -->
<!--       substr(Df_full$DIAG_CODE_4[i], 1, 3) %in% icd_10_death | -->
<!--       substr(Df_full$DIAG_CODE_5[i], 1, 3) %in% icd_10_death ) { -->
<!--     Df_full$icd_death[i] <- 1 -->
<!--   }  -->
<!-- } -->
<!-- ``` -->

<!-- ```{r} -->
<!-- icd_10_death <- c("O95", "O96", "O97", "R96", "R97", "R98", "R99") -->
<!-- Df_full %>% select(substr(Df_full$DIAG_CODE_1[i], 1, 3) %in% icd_10_death |  -->
<!--                    substr(Df_full$DIAG_CODE_2[i], 1, 3) %in% icd_10_death | -->
<!--                    substr(Df_full$DIAG_CODE_3[i], 1, 3) %in% icd_10_death | -->
<!--                    substr(Df_full$DIAG_CODE_4[i], 1, 3) %in% icd_10_death | -->
<!--                    substr(Df_full$DIAG_CODE_5[i], 1, 3) %in% icd_10_death) -->
<!-- ``` -->



