---
title: "Manuscript Results"
output:
  pdf_document: default
  html_document: default
  word_document: default
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning=F, message=F)
#rm(list = ls())
options(scipen=999)
```

```{r required packages}
require(tidyverse)    # for data manipulation
require(formattable)  # for formatting tables
require(knitr)        # for saving tables
require(scales)       # for ggplot axis labels
library(gridExtra)    # for gridded plots 
require(survival)     # for survival analysis
require(survminer)    # for survival plotting
require(kableExtra)
require(dampack)
require(darthtools)
index <- c(1:1000)
nn <- length(index)
loc_here <- paste0(here::here(),"/")
source(paste0(loc_here,"05_report/report_functions.R"))
```

# Base case

## Scenario #1a

-   Combo vs. chemo as first-line treatment
-   Lifetime duration of combo therapy
-   0% radiation at progression (Post-2014 SickKids data indicates that no patients who received chemo and progressed were radiated)
-   100% combo price
-   Discount rate: 1.5
-   Data source for controls & exposed: Investigator assessment - Bouffet et al., NEJM 2023.
-   \*\*Post-progression risk for subsequent progression = pre-progression risk for first progression in combo arm
-   10,000 individuals
-   1000 simulation runs

\newpage

### Investigator assessment, Targeted curve – Exponential, SoC curve – Exponential

```{r}
scen <- paste0("1a")
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase exp lifetime investigator combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)[[1]]; create_table(res_model)[[2]]
```

```{r, out.width="100%"}
plots <- create_trace(fileloc = fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
plots$ae_plot1
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Investigator assessment, Targeted curve – Log-Normal, SoC curve – Log-Normal

```{r}
scen ="1b"
fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase lnorm lifetime investigator combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)[[1]]; create_table(res_model)[[2]]
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
plots$ae_plot1
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Investigator assessment, Targeted curve – Log-Normal, SoC curve – Exponential

```{r}
scen ="1c"

fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase lnorm exp lifetime investigator combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)[[1]]; create_table(res_model)[[2]]
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
plots$ae_plot1
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Independent reviewer, Targeted curve – Exponential, SoC curve – exponential

```{r}
scen ="1d"

fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase exp lifetime combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model, wtp=600000)[[1]]; create_table(res_model, wtp=600000)[[2]]
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
plots$ae_plot1
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Independent reviewer, Targeted curve – Log-Normal, SoC curve – Log-Normal

```{r}
index = 1:950
nn <- length(index)

scen ="1e"

fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase lnorm lnorm lifetime combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model, wtp=500000)[[1]]; create_table(res_model, wtp=500000)[[2]]
```

```{r, out.width="100%"}
plots <- create_trace(fileloc = fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
plots$ae_plot1
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

## Scenario #1c

-   Combo vs. chemo as first-line treatment
-   Lifetime duration of combo therapy
-   0% radiation at progression (Post-2014 SickKids data indicates that no patients who received chemo and progressed were radiated)
-   **50% combo price reduction**
  -   Discount rate: 1.5
-   Data source for controls & exposed: Investigator assessment - Bouffet et al., NEJM 2023.
-   \*\*Post-progression risk for subsequent progression = pre-progression risk for first progression in combo arm
-   10,000 individuals
-   50 simulation runs

\newpage

### Investigator assessment, Targeted curve – exponential, SoC curve – exponential

```{r}
index = 1:900
nn <- length(index)

scen ="2a"

fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase exp exp lifetime discount combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)[[1]]; create_table(res_model)[[2]]
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
plots$ae_plot1
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

### Investigator assessment, Targeted curve – lognormal, SoC curve – lognormal

```{r}
index = 1:1000
nn <- length(index)

scen ="2b"

fileloc <- here::here("04_analysis","output","scenarios",scen, "basecase lnorm lnorm lifetime discount combo")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)[[1]]; create_table(res_model)[[2]]
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
plots$ae_plot1
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

### Investigator assessment, Targeted curve – exponential, SoC curve – exponential 75% discount

```{r}
index = 1:693
nn <- length(index)

scen ="3b"

fileloc <- here::here("04_analysis","output","scenarios",scen, "/basecase exp exp lifetime discount combo/")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)[[1]]; create_table(res_model)[[2]]
```

```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```

```{r, out.width="100%"}
plots$ae_plot1
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage
### Investigator assessment, Targeted curve – exponential, SoC curve – sickkids no discount


```{r}
index = 1:969
nn <- length(index)

scen ="3a"

fileloc <- here::here("04_analysis","output","scenarios",scen, "/sickkids control invest exp lifetime combo/")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)[[1]]; create_table(res_model)[[2]]
```


\newpage
### Investigator assessment, Targeted curve – exponential, SoC curve – exponential 2 year effect


```{r}
index = 1:1000
nn <- length(index)

scen ="4a"

fileloc <- here::here("04_analysis","output","scenarios",scen, "/basecase exp 2year investigator combo/")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)[[1]]; create_table(res_model)[[2]]
```


```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```














```{r, out.width="100%"}
plots$ae_plot1
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```

\newpage

\newpage
### Investigator assessment, Targeted curve – exponential, SoC curve – exponential 3 year effect


```{r}
index = 1:800
nn <- length(index)

scen ="4b"

fileloc <- here::here("04_analysis","output","scenarios",scen, "/basecase exp 3year investigator combo/")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)[[1]]; create_table(res_model)[[2]]
```


```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```


```{r, out.width="100%"}
plots$ae_plot1
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```




\newpage

### Investigator assessment, Targeted curve – exponential, SoC curve – exponential zero discounting


```{r}
index = 1:1000
nn <- length(index)

scen ="4a"

fileloc <- here::here("04_analysis","output","scenarios",scen, "/basecase exp exp lifetime zerodiscounting combo/")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)[[1]]; create_table(res_model)[[2]]
```


```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```


```{r, out.width="100%"}
plots$ae_plot1
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```



\newpage

### Investigator assessment, Targeted curve – exponential, SoC curve – exponential 3% discounting


```{r}
index = 1:1000
nn <- length(index)

scen ="4a"

fileloc <- here::here("04_analysis","output","scenarios",scen, "/basecase exp exp lifetime threediscounting combo/")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)[[1]]; create_table(res_model)[[2]]
```


```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```


```{r, out.width="100%"}
plots$ae_plot1
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```



\newpage

### Investigator assessment, Targeted curve – exponential, SoC curve – exponential lifelong costs 


```{r}
index = 1:1000
nn <- length(index)

scen ="5a"

fileloc <- here::here("04_analysis","output","scenarios",scen, "//basecase exp exp lifetime lifelongcost combo/")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)[[1]]; create_table(res_model)[[2]]
```


```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```


```{r, out.width="100%"}
plots$ae_plot1
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```






\newpage

### Investigator assessment, Targeted curve – exponential, SoC curve – exponential 20% radiation  


```{r}
index = 1:136
nn <- length(index)

scen ="6a"

fileloc <- here::here("04_analysis","output","scenarios",scen, "//basecase exp exp lifetime rad combo/")
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[index]
```

```{R}
create_table(res_model)[[1]]; create_table(res_model)[[2]]
```


```{r, out.width="100%"}
plots <- create_trace(fileloc)
plots$trace_plot
```


```{r, out.width="100%"}
plots$ae_plot1
```

```{r, out.width="100%"}
grid.arrange(plots$surv_plot1, plots$surv_plot2, plots$surv_plot3, nrow=3)
```





